Visualization and analysis of probability distributions of large temporal data

### 2021-11-16 Rmd/02-gravitas.Rmd
Update 02-gravitas.Rmd

In \autoref{fig:bothcust}b, the black line is the median, whereas the purple (narrow) band covers the 25th to 75th percentile, the orange (middle) band covers the 10th to 90th percentile, and the green (broad) band covers the 1st to 99th percentile. The first facet represents the weekday behavior while the second facet displays the weekend behavior; energy consumption across each hour of the day is shown inside each facet. The energy consumption is extremely skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer compared to weekends.

>>>>

In \autoref{fig:bothcust}b, the black line is the median, the purple (narrow) band covers the 25th to 75th percentile, the orange (middle) band covers the 10th to 90th percentile, and the green (broad) band covers the 1st to 99th percentile. The first facet represents the weekday behavior while the second facet displays the weekend behavior; energy consumption across each hour of the day is shown inside each facet. The energy consumption is extremely skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer compared to weekends.
